### 2018-02-01 includes/introduction.tex
Fixing sticking-out words.

Fuzzing has been used to test all kinds of software
including SAT solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers,
we introduce \fuzzer{} and describe its value
as an exploratory testing tool. We demonstrate its efficacy
by presenting limitations it helped discover in
leading string solvers. To the best of our knowledge, \fuzzer{} is the
only tool aimed at automatic generation of string constraints. \fuzzer{} can
be used to mutate or transform existing benchmarks, as well as
randomly generate structured instances. These instances can be scaled with
respect to a variety of parameters, e.g., length of string constants,
depth of concatenations (concats) and regular expressions, number of variables,
number of length constraints, and many more.

@@

\begin{enumerate}
    \item \textbf{The \fuzzer{} tool}:
        In Sect.~\ref{sec:fuzzer}, we describe a modular fuzzer that can
        transform and generate \smtfull{} string and regular
        expression (regex) instances.\footnote{We assume basic
        familiarity with string solvers and their input
        language.} Scaling inputs (e.g., long string constants,
        deep concatenations) are particularly useful in identifying asymptotic
        behaviors in solvers, and \fuzzer{} has many options to generate them.
        We briefly document \fuzzer{}'s components and modular architecture.
        We provide example use cases to demonstrate its utility as an
        exploratory solver testing tool.

>>>>

Fuzzing has been used to test all kinds of software
including SAT solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers,
we introduce \fuzzer{} and describe its value
as an exploratory testing tool. We demonstrate its efficacy
by presenting limitations it helped discover in
leading string solvers. To the best of our knowledge, \fuzzer{} is the
only tool aimed at automatic generation of string constraints. \fuzzer{} can
be used to mutate or transform existing benchmarks, as well as
randomly generate structured instances. These instances can be scaled with
respect to a variety of parameters, e.g., length of string constants,
depth of concatenations (concats) and regular expressions (regexes),
number of variables, number of length constraints, and many more.

@@

\begin{enumerate}
    \item \textbf{The \fuzzer{} tool}:
        In Sect.~\ref{sec:fuzzer}, we describe a modular fuzzer that can
        transform and generate \smtfull{} string and regex
        instances.\footnote{We assume basic
        familiarity with string solvers and their input
        language.} Scaling inputs (e.g., long string constants,
        deep concatenations) are particularly useful in identifying asymptotic
        behaviors in solvers, and \fuzzer{} has many options to generate them.
        We briefly document \fuzzer{}'s components and modular architecture.
        We provide example use cases to demonstrate its utility as an
        exploratory solver testing tool.
